Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-21 analysis/paper/paper.Rmd
Add ICC to paper

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "egg",
  "english",
  "extrafont",
  "flextable",
  "ggplot2",
  "ggridges",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "rsvg",
  "tidyr",
  "tools"
)

@@

The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences showed some differences (Figure \@ref(fig:irReproScore)).
The article that had the greatest difference, 13 to 33%, was DOI "10.1007/s12600-021-00902-2" with a standard deviation of `r ir %>% filter(doi == "10.1007/s12600-021-00902-2") %>% summarise(x = round(sd(reproducibility_score), 1))`.
All other articles had standard deviation scores of less than 4 (Table \@ref(tab:interRaterSD)).
However, all article scores largely agreed and fell below 50% (Figure \@ref(fig:irReproScore)).

@@

```{r interRaterSD, echo=FALSE, message=FALSE, warning=FALSE}
ir %>%
  group_by(doi) %>%
  summarise(x = round(sd(reproducibility_score), 1)) %>%
  rename(`Standard Deviation` = x) %>%
  rename(DOI = doi) %>%
  flextable() %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Standard deviation of reproducibility scores for five articles evaluated by all five co-authors to check for differences in article ratings.")
```

>>>>

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "egg",
  "english",
  "extrafont",
  "flextable",
  "ggplot2",
  "ggridges",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "psych",
  "rsvg",
  "tidyr",
  "tools"
)

@@

The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences had moderate reliability, 0.57, (Table \@ref(tab:icc), Figure \@ref(fig:irReproScore)).

@@

```{r icc, echo=FALSE, message=FALSE, warning=FALSE}
ir %>%
  select(doi, assignee, reproducibility_score) %>%
  pivot_wider(names_from = assignee, values_from = reproducibility_score) %>%
  select(Adam, Emerson, Kaique, Nik, Zach) %>%
  as.matrix() %>%
  ICC() %>%
  `[[`(1) %>%
  flextable() %>%
  set_table_properties(layout = "autofit") %>% 
  set_caption("this needs a caption")
```
